Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-04-06 Grassmannian_cells.tex
Added Lemma 2.7 and changed Lemma 2.8

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(n-1)}\cong\tilde P_{m-1}^{(1)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.
  \end{enumerate}
\end{lemma}

\begin{lemma}\label{quotient}
 Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$. If $U\subset P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
\end{lemma}
\begin{proof}
First observe that $\tilde P_m\in ~^\perp \tilde P_{m+1}^{(k-1)}$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$. Assume that $U$ is preprojective with $\Hom(U,\tilde P_{m+1}^{(k-1)})=0$ (check again). This yields $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$. Consider
\[0\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]\longrightarrow[\tilde P_{m+1}^{(k-1)},U]^1\xlongrightarrow{\pi}[\tilde P_{m+1}^{(k-1)},\tilde P_m]^1\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]^1\longrightarrow 0.\]
Since $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$, we have that $\pi$ is surjective if $\pi\neq 0$. If $U=U_1\oplus\ldots\oplus U_r$ is a decomposition into indecomposable representations, we can write $\pi=(\pi_1,\ldots,\pi_r)$ and it suffices to show that $\pi_j\neq 0$ for at least one $j=1,\ldots,r$. Thus we can without loss of generality assume that $U$ is indecomposable (check again). This means that $U\cong \tilde P_{i}$ for some $i=1,\ldots,m$. Moreover, $\tilde P_{m+1}/U$ is indecomposable (details).

If $\tilde P_{m+1}/U$ is exceptional, $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$ together with \cite[Theorem 4.1]{sch} yields that either $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$ or $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$. Thus $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)\neq 0$ would imply that $\Ext(\tilde P_{m+1}^{(k-1)},U)=0$. But this contradicts the assumption and the claim follows.

Thus assume that $\tilde P_{m+1}/U$ has self-extensions. Since $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})= 0$, from \cite[Lemma 4.1]{hr} we obtain that every homomorphism $\tilde P_{m+1}^{(k-1)}\to \tilde P_m/U$ is injective or surjective. By a dimension count it needs to be surjective (case $k=1$?). Such a homomorphism would yield $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})\twoheadrightarrow\Ext(\tilde P_m/U,\tilde P_m/U)\neq 0$ which contradicts the further observations. Thus $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, already yields $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ in this case.

Case $\Hom(U,P)\neq 0$?

>>>>

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(n-1)}\cong\tilde P_{m-1}^{(1)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.
  \end{enumerate}
\end{lemma}
\begin{lemma}\label{AR}
Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$
There exists a short exact sequence 
\[\ses{\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}}{\tilde P_m}{\tau\tilde P_{m+1}^{(k-1)}}\]
where $\tau$ denotes the Auslander-Reiten translate. Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$.
\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Idea: Check this for $m=1$ or $m=2$ and apply BGP-reflections.
\end{proof}
\begin{lemma}\label{quotient}
 Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$. If $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
\end{lemma}
\begin{proof}
Idea: Every $U\subset \tilde P_m$ gives rise to a diagram
  \[\xymatrix{0\ar[r] &\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]

	If $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, we have $W\neq 0$. Thus $\tau\tilde P_{m+1}^{(k-1)}/W$ is a proper factor. It follows that we have $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)=0$ by Auslander-Reiten-theory and because 
$\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$.

Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})=0$, it follows $\Ext(\tilde P_{m+1}^{(k-1)},(\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})/V)=0$. The first statement should be a consequence of Lemma \ref{AR}. This yields the claim.

%First observe that $\tilde P_m\in ~^\perp \tilde P_{m+1}^{(k-1)}$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$. Assume that $U$ is preprojective with $\Hom(U,\tilde P_{m+1}^{(k-1)})=0$ (check again). This yields $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$. Consider
%\[0\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]\longrightarrow[\tilde P_{m+1}^{(k-1)},U]^1\xlongrightarrow{\pi}[\tilde P_{m+1}^{(k-1)},\tilde P_m]^1\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]^1\longrightarrow 0.\]
%Since $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$, we have that $\pi$ is surjective if $\pi\neq 0$. If $U=U_1\oplus\ldots\oplus U_r$ is a decomposition into indecomposable representations, we can write $\pi=(\pi_1,\ldots,\pi_r)$ and it suffices to show that $\pi_j\neq 0$ for at least one $j=1,\ldots,r$. Thus we can without loss of generality assume that $U$ is indecomposable (check again). This means that $U\cong \tilde P_{i}$ for some $i=1,\ldots,m$. Moreover, $\tilde P_{m+1}/U$ is indecomposable (details).
%
%If $\tilde P_{m+1}/U$ is exceptional, $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$ together with \cite[Theorem 4.1]{sch} yields that either $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$ or $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$. Thus $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)\neq 0$ would imply that $\Ext(\tilde P_{m+1}^{(k-1)},U)=0$. But this contradicts the assumption and the claim follows.
%
%Thus assume that $\tilde P_{m+1}/U$ has self-extensions. Since $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})= 0$, from \cite[Lemma 4.1]{hr} we obtain that every homomorphism $\tilde P_{m+1}^{(k-1)}\to \tilde P_m/U$ is injective or surjective. By a dimension count it needs to be surjective (case $k=1$?). Such a homomorphism would yield $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})\twoheadrightarrow\Ext(\tilde P_m/U,\tilde P_m/U)\neq 0$ which contradicts the further observations. Thus $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, already yields $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ in this case.
%
%Case $\Hom(U,P)\neq 0$?
